\bf Nonparametric Bootstrap Kolmogorov-Smirnov Goodness-of-Fit Test for Marginal Distributions of Stationary Time Series

### 2024-03-16 manuscript/manuscript.tex
10000 replicates

Using the \textsl{tseries} package 
\citep{tseries}, 
we gathered closing stock prices for the S\&P 500 index. We
observed how the method performs using increasingly smaller durations of
time.
We used the last 5 years of data: January 1st, 2019 to December 31st, 2023,
4 years of data: January 1st, 2020 to December 31st, 2023,
3 years of data: January 1st, 2021 to December 31st, 2023,
2 years of data: January 1st, 2022 to December 31st, 2023,
and 1 year of data: January 1st, 2023
to December 31st, 2023.
We approximated stock returns by taking the difference in the logarithm 
of the closing prices.
We tested that the stock returns are normally
distributed and Student's $t$ distributed 
with degrees of freedom $v \in \{30, 20, 10, 5, 4, 3, 2, 1\}$.
The p-values for these tests are highlighted in 
Tables~\ref{table:SP5001}--\ref{table:SP5005}.

@@

While we expect there to be differences in the p-values for the different 
methods, in this example, there are many instances where the conclusions
at the .05 significance level for our method are different than those
for both
\citep{babu2004goodness}'s and \citet{zeimbekakis2022misuses}'s method.
For instance, for a duration of 4 years, our method fails to reject that
the series follows the $v = 5$ Student's $t$ distribution with p-value .064,
wheraeas \citep{babu2004goodness}'s method finds a p-value of .016, and 
\citet{zeimbekakis2022misuses}'s method finds a p-value of .01.

@@

Once again using the \textsl{tseries} package 
\citep{tseries}, 
we gathered closing stock prices for the S\&P 100 index. We varied the
durations as we did with the S\&P 500 index.
We approximated stock returns by taking the difference in the logarithm 
of the closing prices.
We tested that the stock returns are normally
distributed and Student's $t$ distributed 
with degrees of freedom $v \in \{30, 20, 10, 5, 4, 3, 2, 1\}$.
The p-values for these tests are highlighted in 
Tables~\ref{table:SP1001}--\ref{table:SP1005}.
For a duration of 4 years, our method fails to reject that
the series follows the $v = 5$ Student's $t$ distribution with p-value .092,
wheraeas \citep{babu2004goodness}'s method finds a p-value of .031, and 
\citet{zeimbekakis2022misuses}'s method finds a p-value of .027.

>>>>

Using the \textsl{tseries} package 
\citep{tseries}, 
we gathered closing stock prices for the S\&P 500 index. We
observed how the method performs using increasingly smaller durations of
time.
We used the last 5 years of data: January 1st, 2019 to December 31st, 2023,
4 years of data: January 1st, 2020 to December 31st, 2023,
3 years of data: January 1st, 2021 to December 31st, 2023,
2 years of data: January 1st, 2022 to December 31st, 2023,
and 1 year of data: January 1st, 2023
to December 31st, 2023.
We approximated stock returns by taking the difference in the logarithm 
of the closing prices.
We tested that the stock returns are normally
distributed and Student's $t$ distributed 
with degrees of freedom $v \in \{30, 20, 10, 5, 4, 3, 2, 1\}$.
We used $B = 10,000$ bootstrap 
replicates in this analysis.
The p-values for these tests are highlighted in 
Tables~\ref{table:SP5001}--\ref{table:SP5005}.

@@

While we expect there to be differences in the p-values for the different 
methods, in this example, there are many instances where the conclusions
at the .05 significance level for our method are different than those
for both
\citep{babu2004goodness}'s and \citet{zeimbekakis2022misuses}'s method.
For instance, for a duration of 4 years, our method fails to reject that
the series follows the $v = 5$ Student's $t$ distribution with p-value .061,
wheraeas \citep{babu2004goodness}'s method finds a p-value of .0222, and 
\citet{zeimbekakis2022misuses}'s method finds a p-value of .0141. Although this
will not always be the case, we have found at least one example of a difference
in conclusions for different methods.

@@

Once again using the \textsl{tseries} package 
\citep{tseries}, 
we gathered closing stock prices for the S\&P 100 index. We varied the
durations as we did with the S\&P 500 index.
We approximated stock returns by taking the difference in the logarithm 
of the closing prices.
We tested that the stock returns are normally
distributed and Student's $t$ distributed 
with degrees of freedom $v \in \{30, 20, 10, 5, 4, 3, 2, 1\}$. 
We used $B = 10,000$ bootstrap 
replicates in this analysis as well.
The p-values for these tests are highlighted in 
Tables~\ref{table:SP1001}--\ref{table:SP1005}. One can observe more examples
of our method reaching different conclusions at the .05 level than others.
For a duration of 4 years, our method fails to reject that
the series follows the $v = 5$ Student's $t$ distribution with p-value .0873,
wheraeas \citep{babu2004goodness}'s method finds a p-value of .0368, and 
\citet{zeimbekakis2022misuses}'s method finds a p-value of .03. we have here
another instance where using a different method would lead to a different
conclusion about the marginal distribution of the population of interest.
